Individual Stellar Halos of Massive Galaxies Measured to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-07-03 draft/paper1_v13.tex
Final edits

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Jenny E. Greene,$^{4}$
        Kevin Bundy,$^{3,1}$
        \newauthor
        Yen-Ting Lin,$^{5}$
        Masayuki Tanaka,$^{5}$
        Rachel Mandelbaum,$^{7}$
        Satoshi Miyazaki,$^{5,8}$
        \newauthor
        Yutaka Komiyama$^{5,8}$
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
              Tokyo 181--8588, Japan\\
        $^{6}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{7}$McWilliams Center for Cosmology, Department of Physics, 
              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
        $^{8}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
              Tokyo, 181--8588, Japan
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

    Following this initial epoch of early formation, feedback from stars and/or AGN 
    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quenches star formation in 
    massive galaxies. 
    A large fraction of these massive progenitors are already quiescent by $z=1$ 
    (e.g. \citealt{Bezanson2009, Kriek2016}). 
    The second phase of their assembly is driven by non-dissipative processes such 
    as dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
    The ``two-phase'' formation of massive galaxies is designed to both explain the 
    observed increase in the effective radii ($R_{\mathrm{e}}$) of massive galaxies 
    (e.g. \citealt{Newman2012, vdWel2014}) and the build-up of stellar 
    halos  (e.g. \citealt{Szomoru2012, Patel2013}). 
    According to this formation mechanism, minor mergers dominate the mass assembly 
    of massive galaxies at late times 
    (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, Laporte2013}).

@@

    Until now, studies of the surface brightness or mass density profiles of massive 
    galaxies have been either conducted using large samples but with shallow imaging, 
    for example the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}), 
    or with deeper imaging but much smaller sample sizes (e.g \citealt{Gonzalez2005, 
    Capaccioli2015}). 
    In this paper, we take advantage of new high-quality (median seeing of
    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$~\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to characterize the light profiles of massive 
    galaxies out to 100 kpc. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    We select a large sample (${\sim} 7000$) of massive central galaxies 
    at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.

@@

    In this paper, we use this sample to 
    (a) reliably measure individual surface mass density (\mden{}) profiles of 
    massive galaxies out to 100 kpc, 
    (b) investigate the dependence of their outer stellar halos on total stellar 
    mass, and 
    (c) examine the implications in terms of evaluating the high mass end of the 
    galaxy stellar mass function (SMF). 
    In a second paper in this series, we will investigate the environmental 
    (dark matter halo mass) dependence of the sizes of massive ETGs 
    (Huang\etal in prep.).

@@

    Finally, we emphasize that in this work, we do not attempt to disentangle the 
    galaxy light from any ``intra-cluster'' light component (ICL; e.g. 
    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). 
    Although the rising stellar velocity dispersion in the outskirt of massive 
    brightest cluster galaxy (BCG)
    hints a kinematically separated ICL component (e.g. 
    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}),
    it is extremely difficult to reliably isolate them photometrically.
    Moreover, both the stellar halo of main galaxy and the ICL component carry 
    important information regarding the assembly history of central galaxy and its 
    dark matter halo. 
    Therefore, we adopt the view that the light of the main galaxy and the 
    ICL component share a smooth and continuous distribution.

@@

    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in terms of 
    the $i$-band surface brightness limit than SDSS. 
    Combined with the excellent imaging resolution (the median $i$-band seeing is 
    0.6\asec) and the wide area, the HSC survey represents an ideal dataset to perform 
    statistical studies of the surface brightness profiles of massive galaxies out to 
    their very outskirts.  
    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
    for three low redshift ETGs, and shows that HSC survey data are well suited for 
    mapping the stellar distribution of massive galaxies out to large radii.

@@

    The pixel scale of the combined images is $0.168$\asec{}. 
    Photometric calibration is based on data from the Panoramic Survey Telescope 
    and Rapid Response System (Pan-STARRS) 1 imaging survey 
    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
    To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
    performs multi-band post-processing at the \texttt{coadd} level. 
    First, \texttt{hscPipe} performs object detection on \texttt{coadd} images in 
    each band independently and records the flux peak and the above-threshold region 
    (referred as a \texttt{footprint}) for each source. 
    Next, \texttt{footprints} and peaks from different bands are merged together before     
    performing deblending and measurements. 
    Finally, \texttt{hscPipe} selects a reference band for each object based on the 
    $S/N$ in different bands (for most galaxies in this work, the reference band is 
    the $i$-band). 
    After fixing the centroids, shape, and other non-amplitude parameters of each 
    object in this reference catalog, \texttt{hscPipe} perform forced photometry 
    on the \texttt{coadd} image in each band. 
    This forced photometry approach is optimized to yield accurate galaxy colors.

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{Bosch2017}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipe}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
    large ETGs where satellites and background galaxies often blend with the low surface 
    brightness stellar envelope is a challenging problem. 
    The deblending method currently implemented in \texttt{hscPipe} tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to an 
    under-estimation of the total flux of massive ETGs (this is discussed further in 
    \citealt{Bosch2017}).  
    For these reasons, our results will be based on custom-developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    1) to perform a first broad sample selection, and 2) to estimate the average 
    color of massive galaxies.

@@

    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
    team.
    It is created by matching HSC objects with a series of publicly available 
    spectroscopic redshifts (e.g.\ SDSS DR12 \citealt{SDSSDR12}; 
    GAMA DR2 \citealt{Liske2015}). 
    The spec-$z$ quality flag from different catalogs are homogenized into a single 
    flag that indicates secure redshifts.
    Please see \S~4.4.2 of \citet{HSC_DR1} for details of this catalog.  
    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
    the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

    Objects without a spectroscopic redshift are matched with central 
    galaxies from the \redm{} SDSS DR8 (\citealt{Rykoff2014}) catalog using a 
    $2.0^{\arcsec}$ matching radius. 
    Matched objects with a red-sequence photo-$z$ ($0.3 \leq z_{\lambda} < 0.5$) are 
    included in our sample. 
    The accuracy of the red-sequence photo-$z$ is sufficient (median 
    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$) for our goal.
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

@@

    The surface brightness profiles of massive ETG are not well modeled by the 
    de~Vaucouleurs or single-\ser law, especially at the imaging depth of HSC.
    These models will fail to simultaneously describe the profile in both the inner 
    and the outer regions and also cannot account for any radial variations in 
    ellipticity and position angle. 
    In principle, massive galaxies can still be described by more complex 
    models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but they are still 
    sensitive to the choice of a particular model (e.g. de~Vaucouleurs or \ser{} 
    profile), the number of components, initial guesses of parameters, and internal 
    degeneracies among different parameters. 
    Background subtraction uncertainties can also affect the 2-D model fitting method, 
    especially for the massive ETGs that make up our sample.

    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
    galaxies and to measure their one-dimensional stellar mass surface 
    density profiles (\mden{}). 
    This 1-D method is less affected by the issues mentioned above. 
    Also, we will only study galaxies in the radial range where we are less 
    sensitive to either the PSF or the background subtraction.
    We ignore the inner 6.11 kpc, which is twice the size of 1\asec{} seeing at 
    $z=0.5$.
    Using this conservative choice, we can safely ignore the smearing effect of 
    seeing outside this radius.
    As we will show later, we confirm this by comparing our HSC profiles with 
    observations with higher spatial resolution. 
    As for the impact from background subtraction, we will focus on the profiles 
    within 100 kpc.

    We prepare large $i$-band postage-stamps for each galaxy that extend to 750 kpc 
    in radius, along with a bad pixel mask and the PSF model. 
    These postage-stamps include all of the light of the galaxy and are also large 
    enough to also evaluate the background level. We choose to use $i$-band images 
    because they trace the stellar mass distributions of massive galaxies at 
    $0.3 \leq z \leq 0.5$ reasonably well 
    (the observed $i$-band corresponds to a rest-frame $g$ or $r$ band), but also 
    because they have better seeing and much lower background levels than the $z$ 
    and $y$ band images (although these in principle may be better tracers of 
    \mden{}).

    For each cut-out, to overcome the \texttt{hscPipe} ``over-deblending'' issue, 
    we use a customized procedure to detect and aggressively mask out
    neighbouring objects. 
    Furthermore, \texttt{hscPipe} tends to over-subtract the background around 
    bright objects. 
    To improve the background subtraction, we first aggressively mask 
    out all objects (including the central massive galaxy), and derive an 
    empirical background correction using \texttt{SExtractor}.
    These procedures are described in details in Appendix~\ref{app:ellipse}. 
    We should point out that we are not using the photometric results from our 
    customized process, but simply rely on them for improved local background model
    and appropriate object mask.

@@

    For physical (e.g.\ late-stage major merger) and nuisance (e.g.\ nearby foreground 
    galaxy or bright star) reasons, we cannot extract reliable 1-D profiles for a small 
    fraction of massive galaxies because they are heavily masked out. 
    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
    the sample.
    %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
    %\nbcg{} sample. 
    We visually examine the 3-color images of randomly selected galaxies with failed 
    1-D profile.  
    Most of them are relative small galaxies that are severely contaminated by nearby 
    objects, and will not affect the results of this work.  
    Meanwhile, it is worth noting that this does exclude most major merging systems 
    among massive galaxies.

    Given our exquisite profiles that extend to 100 kpc, the definition and meaning 
    of ``total'' magnitude (and stellar mass) becomes nuanced.
    With the help of the average \m2l{} estimated in the next section 
    (\S \ref{sec:mstar}), we integrate the profile to a range of radii, and estimate 
    the stellar mass within these different apertures.  
    Motivated by the two-phase scenario, we will consider two benchmark physical 
    apertures throughout this work:

@@

        \item \textbf{The \mstar{} within the inner 10 kpc} 
            (hereafter noted \minn{}). 
            According to the two-phase scenario, the \textit{in situ} star-formation 
            phase quickly builds up the inner, dense core of massive ETGs.  
            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and 
            simulations (e.g. \citealt{RodriguezGomez2016}), the \textit{in situ} 
            component dominates the \mstar{} within one effective radius 
            ($R_{\mathrm{e}}$, or 5-10 kpc) of $z{\sim}0$ massive ETGs.
            We therefore use \minn{} as proxy for the mass forged during the 
            \textit{in situ} phase. 
            Given the quality of the HSC data, we can reliably measure \minn{} over 
            our redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshifts 0.3 and 0.5 respectively).  
            It is worth noting that, at the very high-\mstar{} end, accreted stars 
            may make a significant contribution to the mass within 10 kpc 
            (e.g. \citealt{RodriguezGomez2016}). 
            We will further discuss the justification of this assumption in 
            \ref{ssec:twophase}.

        \item \textbf{The stellar mass within 100 kpc} 
            (hereafter noted \mtot{}). 
            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
            $\times R_{\mathrm{e}}$. 
            We show in \S~\ref{ssec:mtotal} that most of the \mstar{} for 
            these ETGs can be captured by a 100 kpc radius and that \mtot{} is 
            a good proxy for the ``total'' \mstar{}. 
            Although not perfect, we argue that our measurements of \mtot{} (which are 
            actually measuring the light directly out to 100 kpc) are a better tracer 
            of total \mstar{} than model-dependent results from shallower data 
            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
            out to large radii.

@@

    We should point out that both \minn{} and \mtot{} are measured within the same 
    elliptical aperture. 
    The 10 kpc and 100 kpc here refer to the radius along the major axis of the 
    elliptical isophote.

@@

    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes 
    corrected for Galactic extinction. 
    Right now, \cmodel{} only accounts for the statistical error on the flux 
    measurement and it certainly underestimates the true flux errors of bright 
    galaxies.  
    For this work, we supply \texttt{iSEDFit} with simplified flux errors assuming 
    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$ and $y$ band 
    (on average, images in $gy$ bands are shallower in depth and/or have higher 
    background noise).  
    These empirical \s2n{} choices still only provide lower-limits of the true 
    systematic uncertainties from the model-fitting process. 
    In \citealt{SynPipe}, we evaluate the accuracy of HSC \cmodel{} photometry 
    using synthetic galaxies, and show that \cmodel{} provides excellent measurements 
    of five-band colors, which are crucial for reliable \m2l{} estimates.
    The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$.

@@

    Color gradients will be discussed more in \S~\ref{ssec:ell_color}. 
    In summary, our results about the mass-dependence of \mden{} profiles should not 
    be affected by the assumption of a constant \m2l{} ratio because optical color 
    gradients in our sample do not show a dependence on stellar mass.

@@

    As the next step, we want to construct a sample of central galaxies living in halos 
    with \logmh{}$<14.0$. 
    To achieve this, we identify and remove all galaxies within a cylindrical region 
    around all \redm{} clusters. 
    We use a radius equal to $R_{\mathrm{200b}}$ and the thickness of the cylinder is 
    set to twice the value of the photometric redshift uncertainty of each cluster.

>>>>

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Jenny E. Greene,$^{4}$
        Kevin Bundy,$^{3,1}$
        \newauthor
        Yen-Ting Lin,$^{5}$
        Masayuki Tanaka,$^{5}$
        Satoshi Miyazaki,$^{5,7}$
        \newauthor
        Yutaka Komiyama$^{5,7}$
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo, Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
              Tokyo 181--8588, Japan\\
        $^{6}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{7}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
              Tokyo, 181--8588, Japan
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

    Following the initial phase of growth, feedback from stars and/or AGN 
    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quenches star formation in 
    massive galaxies. 
    A large fraction of these massive progenitors are already quiescent by $z=1$ 
    (e.g. \citealt{Bezanson2009, Kriek2016}). 
    The second phase of their assembly is driven by non-dissipative processes such 
    as dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
    The ``two-phase'' formation of massive galaxies help explain both the 
    observed increase in the effective radii ($R_{\mathrm{e}}$) of massive galaxies 
    (e.g. \citealt{Newman2012, vdWel2014}) and the build-up of stellar 
    halos  (e.g. \citealt{Szomoru2012, Patel2013}). 
    It also posits that minor mergers dominate the mass assembly 
    of massive galaxies at late times 
    (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, Laporte2013}).

@@

    Until now, studies of the surface brightness or mass density profiles of massive 
    galaxies have been either conducted using large samples but with shallow imaging, 
    for example the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}), 
    or with deeper imaging but much smaller sample sizes (e.g \citealt{Gonzalez2005, 
    Capaccioli2015}). 
    In this paper, we take advantage of new high-quality (median seeing of
    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$~\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to characterize the light profiles of massive 
    galaxies out to 100 kpc. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    ideal for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    We select a large sample (${\sim} 7000$) of massive central galaxies 
    at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.

@@

    In this paper, we use this sample to 
    (a) reliably estimate individual surface mass density (\mden{}) profiles of 
    massive galaxies out to 100 kpc, 
    (b) investigate the dependence of their outer stellar halos on total stellar 
    mass, and 
    (c) examine the implications in terms of evaluating the high mass end of the 
    galaxy stellar mass function (SMF). 
    In a second paper in this series, we will investigate the environmental 
    (dark matter halo mass) dependence of the sizes of massive ETGs 
    (Huang\etal in prep.).

@@

    Finally, we emphasize that in this work, we do not attempt to disentangle the 
    galaxy light from any ``intra-cluster'' light component (ICL; e.g. 
    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). 
    Although the rising stellar velocity dispersion in the outskirts of massive 
    brightest cluster galaxy (BCG)
    hints at a kinematically separated ICL component (e.g. 
    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}),
    it is extremely difficult to reliably isolate them photometrically.
    Moreover, both the stellar halo of main galaxy and the ICL component carry 
    important information regarding the assembly history of central galaxy and its 
    dark matter halo. 
    Therefore, we adopt the view that the light of the main galaxy and the 
    ICL component trace different scales of a single, smooth, and continuous 
    distribution.

@@

    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in terms of 
    the $i$-band surface brightness limit than SDSS. 
    Combined with the excellent imaging resolution (the median $i$-band seeing is 
    0.6\asec) and the wide area, the HSC survey represents an ideal dataset to perform 
    statistical studies of the surface brightness profiles of massive galaxies out to 
    their distant outskirts.  
    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
    for three low redshift ETGs, and shows that HSC survey data are well suited for 
    mapping the stellar distribution of massive galaxies out to large radii.

@@

    The pixel scale of the combined images is $0.168$\asec{}. 
    Photometric calibration is based on data from the Panoramic Survey Telescope 
    and Rapid Response System (Pan-STARRS) 1 imaging survey 
    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
    To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
    performs multi-band post-processing at the \texttt{coadd} level. 
    First, \texttt{hscPipe} performs object detection on \texttt{coadd} images in 
    each band independently and records the flux peak and the above-threshold region 
    (referred as a \texttt{footprint}) for each source. 
    Next, \texttt{footprints} and peaks from different bands are merged together before     
    performing deblending and measurements. 
    Finally, \texttt{hscPipe} selects a reference band for each object based on the 
    $S/N$ in different bands (for most galaxies in this work, the reference band is 
    the $i$-band). 
    After fixing the centroids, shape, and other non-amplitude parameters of each 
    object in this reference catalog, \texttt{hscPipe} performs forced photometry 
    on the \texttt{coadd} image in each band. 
    This forced photometry approach is optimized to yield accurate galaxy colors
    at $i_{\mathrm{CModel}\leq25.0}$ mag (see \citealt{SynPipe}).

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{Bosch2017}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced multi-band 
    photometry which means that it can accurately measure both the 
    \textit{fluxes and colors of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipe}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
    large ETGs where satellites and background galaxies often blend with the low surface 
    brightness stellar envelope is a challenging problem. 
    The deblending method currently implemented in \texttt{hscPipe} tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to an 
    under-estimation of the total flux of massive ETGs (this is discussed further in 
    \citealt{Bosch2017}).  
    For these reasons, our results will be based on custom-developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    1) to perform a first broad sample selection, and 2) to estimate the average 
    color of massive galaxies.

@@

    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
    team.
    It is created by matching HSC objects with a series of publicly available 
    spectroscopic redshifts (e.g.\ SDSS DR12 \citealt{SDSSDR12}; 
    GAMA DR2 \citealt{Liske2015}). 
    The spec-$z$ quality flags from different catalogs are homogenized into a single 
    flag that indicates secure redshifts.
    Please see \S~4.4.2 of \citet{HSC_DR1} for details of this catalog.  
    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
    the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

    Objects without a spectroscopic redshift are matched with central 
    galaxies from the \redm{} SDSS DR8 (\citealt{Rykoff2014}) catalog using a 
    $2.0^{\arcsec}$ matching radius. 
    Matched objects with a red-sequence photo-$z$ ($0.3 \leq z_{\lambda} < 0.5$) are 
    included in our sample. 
    The accuracy of the red-sequence photo-$z$ is sufficient (median 
    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$) for our purpose.
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

@@

    The surface brightness profiles of massive ETG are not well modeled by the 
    de~Vaucouleurs or single-\ser law, especially at the imaging depth of HSC.
    These models will fail to simultaneously describe the profile in both the inner 
    and the outer regions and also cannot account for any radial variations in 
    ellipticity and position angle. 
    In principle, massive galaxies can still be described by more complex 
    models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but the results are still 
    sensitive to the choice of a particular model (e.g. de~Vaucouleurs or \ser{} 
    profile), the number of components, initial guesses of parameters, and internal 
    degeneracies among different parameters. 
    Background subtraction uncertainties can also affect the 2-D model fitting method, 
    especially for the massive ETGs that make up our sample.

    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
    galaxies and to measure their one-dimensional stellar mass surface 
    density profiles (\mden{}). 
    This 1-D method is less affected by the issues mentioned above. 
    Also, we will only study galaxies in the radial range where we are less 
    sensitive to either the PSF or the background subtraction.
    We ignore the inner $\sim6$ kpc, which is twice the size of 1\asec{} seeing at 
    $z=0.5$.
    Using this conservative choice, we can safely ignore the smearing effect of 
    seeing outside this radius.
    As we will show later, we confirm this by comparing our HSC profiles with 
    observations with higher spatial resolution. 
    As for the impact from background subtraction, we will focus on the profiles 
    within 100 kpc. 
    This is an empirical, but also conservative choice based on the tests we 
    conducted on background-corrected postage-stamps. 
    Once the surrounding objects are appropriately masked out, the extracted 1-D 
    surface brightness profiles rarely see unphysical truncation or fluctuation 
    within 100 kpc, especially for the \logmtot{}$>11.6$ galaxies. 
    Please see Appendix~\ref{app:ellipse} for more details on these tests.

    We prepare large $i$-band postage-stamps for each galaxy that extend to 750 kpc 
    in radius, along with a bad pixel mask and the PSF model. 
    These postage-stamps include all of the light of the galaxy and are also large 
    enough to evaluate the background level. We choose to use $i$-band images 
    because they trace the stellar mass distributions of massive galaxies at 
    $0.3 \leq z \leq 0.5$ reasonably well 
    (the observed $i$-band corresponds to a rest-frame $g$ or $r$ band), but also 
    because they have better seeing and much lower background levels than the $z$ 
    and $y$ band images (although these in principle may be better tracers of 
    \mden{}).

    For each cut-out, to overcome the \texttt{hscPipe} ``over-deblending'' issue, 
    we use a customized procedure to detect and aggressively mask out
    neighbouring objects. 
    Furthermore, \texttt{hscPipe} tends to over-subtract the background around 
    bright objects. 
    To improve the background subtraction, we first aggressively mask 
    out all objects (including the central massive galaxy), and derive an 
    empirical background correction using \texttt{SExtractor}.
    These procedures are described in detail in Appendix~\ref{app:ellipse}. 
    We should point out that we are not using the photometric results from our 
    customized process, but simply rely on them for improved local background model
    and appropriate object mask.

@@

    We cannot extract reliable 1-D profiles for a small fraction of massive galaxies 
    because they are heavily masked out for either physical 
    (e.g.\ late-stage major merger) or nuisance (e.g.\ nearby foreground 
    galaxy or bright star) reasons. 
    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
    the sample.
    %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
    %\nbcg{} sample. 
    We visually examine the 3-color images of randomly selected galaxies with failed 
    1-D profiles.  
    Most of them are relative small galaxies that are severely contaminated by nearby 
    objects, and will not affect the results of this work.  
    Meanwhile, it is worth noting that this does exclude most major merging systems 
    among massive galaxies.

    Given exquisite profiles extending to 100 kpc, the definition and meaning 
    of ``total'' magnitude (and stellar mass) becomes nuanced.
    With the help of the average \m2l{} estimated in the next section 
    (\S \ref{sec:mstar}), we integrate the profile to a range of radii, and estimate 
    the stellar mass within these different projected 2-D apertures.  
    Motivated by the two-phase scenario, we will consider two benchmark physical 
    apertures throughout this work:

@@

        \item \textbf{The \mstar{} within the inner 10 kpc} 
            (hereafter noted \minn{}). 
            According to the two-phase scenario, the \textit{in situ} star-formation 
            phase quickly builds up the inner, dense core of massive ETGs.  
            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and 
            simulations (e.g. \citealt{RodriguezGomez2016}), the \textit{in situ} 
            component dominates the \mstar{} within one effective radius 
            ($R_{\mathrm{e}}$, or 5-10 kpc) of $z{\sim}0$ massive ETGs.
            We therefore use \minn{} as a proxy for the mass formed during the 
            \textit{in situ} phase. 
            Given the quality of the HSC data, we can reliably measure \minn{} over 
            our redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshifts 0.3 and 0.5 respectively).  
            It is worth noting that, at the very high-\mstar{} end, accreted stars 
            may make a significant contribution to the mass within 10 kpc 
            (e.g. \citealt{RodriguezGomez2016}). 
            We will further discuss the justification of this assumption in 
            \ref{ssec:twophase}.

        \item \textbf{The stellar mass within 100 kpc} 
            (hereafter noted \mtot{}). 
            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
            $\times R_{\mathrm{e}}$. 
            We show in \S~\ref{ssec:mtotal} that most of the total \mstar{} for 
            these ETGs lies within a 100 kpc radius and that \mtot{} is 
            a good proxy for the ``total'' \mstar{}. 
            Although not perfect, we argue that our measurements of \mtot{} (which are 
            actually measuring the light directly out to 100 kpc) are a better tracer 
            of total \mstar{} than model-dependent results from shallower data 
            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
            out to large radii.

@@

    We should point out that both \minn{} and \mtot{} are measured after adopting a 
    isophote with fixed ellipticity and position angle. 
    The 10 kpc and 100 kpc here refer to the radius along the major axis of the 
    elliptical isophote.

@@

    We construct five-band SEDs using the forced-photometry \cmodel{} magnitudes 
    corrected for Galactic extinction. 
    Presently, \cmodel{} only accounts for the statistical error on the flux 
    measurement and it certainly underestimates the true flux errors of bright 
    galaxies.  
    For this work, we supply \texttt{iSEDFit} with simplified flux errors assuming 
    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$ and $y$ band 
    (on average, images in $gy$ bands are shallower in depth and/or have higher 
    background noise).  
    These empirical \s2n{} choices still only provide lower-limits of the true 
    systematic uncertainties from the model-fitting process. 
    In \citealt{SynPipe}, we evaluate the accuracy of HSC \cmodel{} photometry 
    using synthetic galaxies, and show that \cmodel{} provides excellent measurements 
    of five-band colors, which are crucial for reliable \m2l{} estimates.
    The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$.

@@

    Color gradients will be discussed more in \S~\ref{ssec:ell_color}. 
    In summary, our results about the mass dependence of \mden{} profiles should not 
    be affected by the assumption of a constant \m2l{} ratio because optical color 
    gradients in our sample do not show a dependence on stellar mass.

@@

    As a next step, we want to construct a sample of central galaxies living in halos 
    with \logmh{}$<14.0$. 
    To achieve this, we identify and remove all galaxies within a cylindrical region 
    around all \redm{} clusters. 
    We use a radius equal to $R_{\mathrm{200b}}$ and the length of the cylinder is 
    set to twice the value of the photometric redshift uncertainty of each cluster.
